% We feel pleased to have the opportunity of expressing our heartfelt thanks and gratitude to those who all rendered their cooperation in making this report.
% This thesis is performed under the supervision of Dr. M. Shamim Kaiser, Associate professor, Institute of Information Technology (IIT), Jahangirnagar University, Savar, Dhaka. During the work, he has supplied us a number of books, journals, and materials related to the present investigation. Without his help, kind support and generous time spans he has given, we could not perform the project work successfully in due time. 
We are delighted to have the opportunity to share our sincere appreciation and gratitude to those who have all cooperated in the creation of this study. Under the guidance of Dr. M. Shamim Kaiser, Associate Professor, Institute of Information Technology (IIT), Jahangirnagar University, Savar, Dhaka, this research is being carried out. He provided us with a variety of books, papers, and documents related to the ongoing inquiry during his service. We could not effectively execute the project work in due time without his assistance, kind support and gracious time spans he provided.

\vspace{0.25cm}
We would like, first and foremost, to convey our strong and heartfelt appreciation to him for his advice, helpful feedback, support and gracious cooperation. 

\vspace{0.25cm}
Dr. M Mesbahuddin Sarker, Director, IIT, Jahangirnagar University, Savar, Dhaka, is profoundly thankful for his useful guidance that has enabled us to complete the work within the timeline. We would really like, however, to 
Thank you to the other affiliates of the IIT faculty who have supported us, explicitly or implicitly, by offering relevant assistance for the completion of this project.

\vspace{0.25cm}
To all the other resources from which we have sought support, we express our sincere gratitude. We are grateful to those who have aided us in undertaking this work explicitly or implicitly. 

\vspace{0.25cm}
Last but not least, we would like to appreciate all the IIT staff, the University of Jahangirnagar and our mates who have supported us during the work by providing their support and assistance.

% First and foremost, we wish to acknowledge our profound and sincere gratitude to him for his guidance, valuable suggestions, encouragement and cordial cooperation.

% We express our utmost gratitude to Dr. M Mesbahuddin Sarker, Director, IIT, Jahangirnagar University, Savar, Dhaka, for his valuable advice that have encouraged us to complete the work within the time frame. Moreover, we would also like to
% thank the other faculty members of IIT who have helped us directly or indirectly by providing their valuable support in completing this work.

% We express our gratitude to all other sources from where we have found help. We are indebted to those who have helped us directly or indirectly in completing this work.

% Last but not least, we would like to thank all the staff of IIT, Jahangirnagar University and our friends who have helped us by giving their encouragement and cooperation throughout the work.