\chapter{Conclusion and Future work}

\section{Conclusion}
Management of Neuro degenarative Disease is a comprehensive process.In this study,  we proposed a DL framework for the management of NDD with the help of IoT. Since falls are the world's second leading cause of unexpected or unplanned incidents in older people with a neurological condition, we have focused on developing a recurrent neural network-based system in our proposed model which can identify every event of a patient's fall/daily operation utilizing IoT and thereafter submit this information to the designated doctor as well as alert caregivers/family members.Fused information from wearable/portable and imaging (camera) sensors has been used for fall detection in our RNN-based fall detection architecture.For these two data sets, open-labeled and UR data sets are used to train the chosen ML system, RNN, and output is contrasted with two classifiers such as RF and SVM. The performance assessment comparison reveals that the proposed fall detection system based on RNN is worthwhile and outperforms its counterparts.

% In our RNN based fall detection Architecture, fused knowledge from wearable/portable and imaging devices (camera) has been used for the fall detection. 

% Open-labeled and UR data-sets are used to train the preferred ML method,RNN and the performance is compared with two classifier like  RF and SVM for these two data-sets. The comparison of the performance evaluation shows that the proposed RNN based fall detection framework is worthwhile and excels its counterparts. 
%Our system guarantees reduced health insurance prices with good quality. It will provide adequate coordination between patients and care professionals. Our system shows the way of ambient assisted living as caregiver need not to monitor the patient 24/7.
\\
\section{Future Work}
In future we will try to make our project better by adding following things:
\begin{enumerate}
    \item We will incorporate additional management capabilities in this model in order to widen the spectrum and increase reliable experience.
    \item  We will try to integrate home automation and facial expression detection system in our work to make a easier life for NDD patients.
    \item We will also try to make a wearable device as we suggested in our proposed method to collect the patient's health related things to detect there health conditions as well as improve it.
    \item Make an application which will show all the work together for better experience.
\end{enumerate}
 we are hoping for the best that we will integrate all these features in our future work and will try to make a better life for the NDD patients.



